---
title: "HW 2"
author: Michelle Poimboeuf
output: github_document
---
#Problem 1 Setup
Load packages

```{r}
library(tidyverse)
library(readxl)
```

#Problem 1
```{r}
trashwheel_df = 
  read_excel(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "Mr. Trash Wheel",
    range = cell_cols("A:N")) %>% 
  janitor::clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(
    sports_balls = round(sports_balls),
    sports_balls = as.integer(sports_balls)
  )
```

Read precipitation data for 2018 and 2017

```{r}
precip_2018 = 
  read_excel(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2018 Precipitation",
    skip = 1
    ) %>%
  janitor::clean_names() %>% 
  drop_na(month) %>% 
  mutate(year = 2018) %>% 
  relocate(year)
  

precip_2017 = 
  read_excel(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2017 Precipitation",
    skip = 1
  ) %>% 
  janitor::clean_names() %>% 
  drop_na(month) %>% 
  mutate(year = 2017) %>% 
  relocate(year)
```
Combine annual precipitation
 
```{r}
month_df = 
  tibble(
    month_num = 1:12,
    month_name = month.name
  )

precip_df = 
  bind_rows(precip_2018, precip_2017)

left_join(
  precip_df, 
  month_df, 
  by = "month")
```

***rewrite code above to match what he did in class**

This dataset contains information from the Mr. Trashweel trash collector in Baltimore, MD. As trash enters the inner harbor, the trashwheel collects that trash and stores it in a dumptser. The dataset contains information on year, month, and trash collected, include some specific kinds of trash. There are a total of 'nrow(precip_df)'(24) rows in our final dataset. Additional data sheets include month precipitation data.

*****For the available data, the total precipitation in 2018 was XXXXXX, and the median number of sports balls in a dumpster in 2017 was XXX.**
***include rest of info from question 1.  For available data, what was the total precipitation in 2018? What was the median number of sports balls in a dumpster in 2017?**

##Problem 2

retain line, station, name, station latitude / longitude, routes served, entry, vending, entrance type, and ADA compliance

```{r}
transit_df = 
  read_csv("./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv", col_types = "cccddccccccccccccccccclclcccddcc") %>% 
  janitor::clean_names() %>% 
  select(line:entry, vending, ada) %>% 
  mutate(entry = ifelse(entry == "yes", TRUE, FALSE)) %>% 
```

There are 1,868 rows in my dataset, 'transit_df' and 19 columns. My data cleaning steps so far include: using the clean_names function to clean up my variables, using the select function to only keep certain variables (variables from 'line' to 'entry,' in addition to variables 'vending' and 'ada'). I then used the mutate function to change the entry variable from a character to a logical vector. 

***Answer the following questions using these data:
How many distinct stations are there? Note that stations are identified both by name and by line (e.g. 125th St A/B/C/D; 125st 1; 125st 4/5); the distinct function may be useful here.

```{r}
transit_df_tidy = 
  #transit_df %>% 
  #pivot_longer(
   # route1:route11, 
    #names_to = "route", 
    #values_to = "subway",
    #names_prefix = "route") %>% 
  #select(-route) %>% 
#relocate(line, subway, station_name)
transit_df %>%
  distinct(line, station_name, across(contains("route")), .keep_all = TRUE)
```

How many stations are ADA compliant?
What proportion of station entrances / exits without vending allow entrance?
Reformat data so that route number and route name are distinct variables. How many distinct stations serve the A train? Of the stations that serve the A train, how many are ADA compliant?***
