---
title: "HW 2"
author: Michelle Poimboeuf
output: github_document
---
#Problem 1 Setup
Load packages

```{r}
library(tidyverse)
library(readxl)
```

#Problem 1
```{r}
trashwheel_df = 
  read_excel(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "Mr. Trash Wheel",
    range = cell_cols("A:N")) %>% 
  janitor::clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(
    sports_balls = round(sports_balls),
    sports_balls = as.integer(sports_balls)
  )
```

Read precipitation data for 2018 and 2017

```{r}
precip_2018 = 
  read_excel(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2018 Precipitation",
    skip = 1
    ) %>%
  janitor::clean_names() %>% 
  drop_na(month) %>% 
  mutate(year = 2018) %>% 
  relocate(year)
  

precip_2017 = 
  read_excel(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2017 Precipitation",
    skip = 1
  ) %>% 
  janitor::clean_names() %>% 
  drop_na(month) %>% 
  mutate(year = 2017) %>% 
  relocate(year)
  
```
 Combine annual precipitation
 
```{r}
month_df = 
  tibble(
    month_num = 1:12,
    month_name = month.name
  )
precip_df = 
  bind_rows(precip_2018, precip_2017) 

left_join(precip_df, month_df, by = "month")
```
 
This dataset contains information from the Mr. Trashweel trash collector in Baltimore, MD. As trash enters the inner harbor, the trashwheel collects that trash and stores it in a dumptser. The dataset contains information on year, month, and trash collected, include some specific kinds of trash. There are a total of 'nrow(precip_df)'(24) rows in our final dataset. Additional data sheets include month precipitation data. 

***include rest of info from question 1.  For available data, what was the total precipitation in 2018? What was the median number of sports balls in a dumpster in 2017?

##Problem 2

retain line, station, name, station latitude / longitude, routes served, entry, vending, entrance type, and ADA compliance

```{r}
transit_df = 
  read_csv(
    "./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>% 
  janitor::clean_names() %>% 
  select(line:entry, vending, ada) %>% 
  mutate(entry = ifelse(entry == "yes", TRUE, FALSE))
```

